Intersection of non-matching grids of different dimensions

### 2016-09-28 paper_intersections.tex
Some fixes and comments on algorithm1 of 23d.

\subsection{Intersection Triangle-Tetrahedron (2D-3D)}
The intersection of a triangle $S_3$ and a tetrahedron $S_4$ is an $n$-side polygon, $n\le 7$. The sides of the polygon
lies either on sides of $S_3$ or on faces of $S_4$. Thus each vertex (IP) of the polygon
can arise either from side-face intersection, or from edge-triangle intersection, or be a vertex of $S_3$.
So we have to compute at most 12 side-face intersections and at most 6 edge-triangle intersections. However,
to this end we only need to compute 9 \plucker coordinates (3 sides, 6 edges) and 18 permuted inner produts, one for every side-edge pair.
Computation of the intersection polygon consists of two parts: calculation of side-tetrahedron IPs (Algorithm \ref{algo:colect_23_ip_triangle})
provides all IPs on the boundary of $S_3$,
calculation of edge-triangle IPs (Algorithm \ref{algo:collect_23_ip_edges}).
Correct order of the IPs stored in the list $I$ is defined by the tables $F_g(:)$ and $F_p(:)$. Every side of the intersection polygon 
lies either on a side of $S_3$, or on a face, or on an edge of $S_4$. Let us denote $M_3$ the set of sides of $S_3$ and $M_4$ the set of volume,
faces, edges, and vertices of $S_4$. Every side of polygon that lies on $x\in M_3\cup M_4$ is folowed by an IP given by $F_g[x]$ 
and every IP $p$ is folowed by the side that lies on $F_p[p]\in M_3\cup M_4$.

@@

  \DontPrintSemicolon
  \SetKw{continue}{continue}
  \KwIn{input data}
  \KwOut{List of IPs on sorted output data}  
  $F_g(:)=-1,\ F_p(:)=-1$\tcp*{Unset links.} 
  \For{side $s$ of $S_3$}{ 
    $L$ = intersection($s, S_4$)\;
    \lIf{ $\abs{L} = 0$}{\continue}
    \lIf{ $\abs{L} = 1$}{
        append $p$ to $J$
        \continue
    }
    \For{$p$ in $L$}{
        \lIf{$p \ne I[-1]$ }{append $p$ to $I$}
        \nllabel{line:m4_object}
        $p$ lies on $x\in M_4$\; 
        \uIf{$p$ is first in $L$}{
            $F_g[x] = p$,\ $F_p[p] = s$\;
        }
        \Else($p$ is the last in $L$){
            $F_g[s] = p,\ F_p[p] = x$\;
            \nllabel{line:back_link43}
            \lIf{$F_g[x] = -1$}{$F_g[x] = p$}
        }
    }
  }  
  \If{$I[-1] = I[0]$}{
    $x = F_p[I[-1]]$\;
    \If{$F_g[x]]=I[-1]$}{$F_g[x]=I[0]$}
    $F_g[s_2] = I[0]$\;
    remove $I[-1]$
  }
\end{algorithm}

Algorithm \ref{algo:colect_23_ip_triangle} pass through every side $s$ of the triangle $S_3$ computing the line-tetrahedron intersection $L$.
In the regular case we process each of the two IPs in $L$. The IP $p$ is added to the list $I$ unless the last point is the same. 
This condition is effective just for the first IP in $L$ and merge IPs at the same vertex of $S_3$. Then we identify an object $x\in M_4$ the point
$p$ lies on (line \ref{line:m4_object}).

If the vertex $v$ is between sides $s_1$, $s_2$, 
we effectively set $F_g[s_1] = v$, $F_g[y]=v$, $F_p[v] = s_2$. The backward temporary link on the line \ref{line:back_link43} 
is used in Algorithm \ref{algo:collect_23_ip_edges} to fix $F_p[p]$ for the second $p$ lying on an edge or a vertex of $S_4$. The condition deals with the case
when two sides intersect the same object $x\in M_4$.

, we first compute IPs
on the boundary of $S_3$ using the line-tetrahedron intersection algorithm for every side. We store intersections with just single IP ito separate list $J$
and skip filling the connection tables. This happen when the side just touch $S_4$ in edge or vertex. 
These IPs will be rediscovered again in Algorithm \ref{algo:collect_23_ip_edges} with better topological information, however
this is not the case if the touched edge $e$ of $S_4$ is coplanar with $S_3$ and the IP is inside of $e$. 
Therefore we keep a separate list of IPs to deal with this case.

For the intersection $L$ we pass through its IPs.

@@

  \SetKw{And}{And}
  \DontPrintSemicolon
  \KwIn{$I$ with IPs on $S_3$ boundary, partialy filled $F$}
  \KwOut{all IPs in $I$, complete $F$}

>>>>

\subsection{Intersection Triangle-Tetrahedron (2D-3D)}
The intersection of a triangle $S_3$ and a tetrahedron $S_4$ is an $n$-side polygon, $n\le 7$. The sides of the polygon
lie either on sides of $S_3$ or on faces of $S_4$. Thus each vertex (IP) of the polygon
can arise either from side-face intersection, or from edge-triangle intersection, or be a vertex of $S_3$.
So we have to compute at most 12 side-face intersections and at most 6 edge-triangle intersections. However,
to this end we only need to compute 9 \plucker coordinates (3 sides, 6 edges) and 18 permuted inner produts, one for every side-edge pair.
Computation of the intersection polygon consists of two parts: calculation of side-tetrahedron IPs (Algorithm \ref{algo:colect_23_ip_triangle})
provides all IPs on the boundary of $S_3$,
calculation of edge-triangle IPs (Algorithm \ref{algo:collect_23_ip_edges}).
\notePE{The following sentence is somehow weird.. I would say that we store IPs $I$; to sort $I$ during the computation, we use the two tables; at the end, $I$ is ordered correctly.}
Correct order of the IPs, stored in the list $I$, is defined by the \emph{connection tables} $F_g(:)$ and $F_p(:)$. \notePE{The following sentece is a copy of the second sentence is this subsection.} Every side of the intersection polygon 
lies either on a side of $S_3$, or on a face, or on an edge of $S_4$. Let us denote $M_3$ the set of sides of $S_3$ and $M_4$ the set of volume,
faces, edges, and vertices of $S_4$. Every side of polygon that lies on $x\in M_3\cup M_4$ is followed by an IP given by $F_g[x]$ 
and every IP $p$ is followed by the side that lies on $F_p[p]\in M_3\cup M_4$.

@@

  \DontPrintSemicolon
  \SetKw{continue}{continue}
  \KwIn{input data}
  \KwOut{List of IPs on sorted output data}  
  $F_g(:)=-1,\ F_p(:)=-1$\tcp*{Unset links.} 
  \For{side $s$ of $S_3$}{ 
    $L$ = intersection($s, S_4$)\;
    \lIf{ $\abs{L} = 0$}{\continue}
    \lIf{ $\abs{L} = 1$}{
        append $p$ to $J$
        \continue
    }
    \For{$p$ in $L$}{
        \lIf{$p \ne I[-1]$ }{append $p$ to $I$}
        \nllabel{line:m4_object}
        $p$ lies on $x\in M_4$\; 
        \uIf{$p$ is first in $L$}{
            $F_g[x] = p$,\ $F_p[p] = s$\;
        }
        \Else($p$ is the last in $L$){
            $F_g[s] = p,\ F_p[p] = x$\;
            \lIf{$F_g[x] = -1$}{$F_g[x] = p$} \nllabel{line:back_link43}
        }
    }
  }  
  \If{$I[-1] = I[0]$}{
    $x = F_p[I[-1]]$\;
    \If{$F_g[x]]=I[-1]$}{$F_g[x]=I[0]$}
    $F_g[s_2] = I[0]$\;
    remove $I[-1]$
  }
\end{algorithm}

Algorithm \ref{algo:colect_23_ip_triangle} passes through every side $s$ of the triangle $S_3$ and computes the line-tetrahedron intersection $L$.
In the regular case we process each of the two IPs in $L$. The IP $p$ is added to the list $I$ unless the last point is the same. 
This condition is effective just for the first IP in $L$ and merges IPs at the same vertex of $S_3$. Then we identify an object $x\in M_4$ the point
$p$ lies on (line \ref{line:m4_object}). \notePE{I am not sure, if the term 'object' is clear..}

\notePE{Why calling it vertex $v$ instead of IP $p$ here? What is $y$?}
If the vertex $v$ is between sides $s_1$, $s_2$, 
we effectively set connections $F_g[s_1] = v$, $F_g[y]=v$, $F_p[v] = s_2$. The backward temporary link on the line \ref{line:back_link43} 
is used in Algorithm \ref{algo:collect_23_ip_edges} to fix $F_p[p]$ for the second $p$ lying on an edge or a vertex of $S_4$. The condition at the end deals with the case
in which two sides intersect the same object $x\in M_4$.

For the regular intersection $L$, we pass through its IPs, as described above. \notePE{For special cases}, we firstly compute IPs
on the boundary of $S_3$ using the line-tetrahedron intersection algorithm for every side. We store single point intersections into separate list $J$
and skip filling the connection tables. This happens when the side touches $S_4$ at its edge or vertex. 
These IPs will be rediscovered again in Algorithm \ref{algo:collect_23_ip_edges} with better topological information, however
this is not the case if the touched edge $e$ of $S_4$ is coplanar with $S_3$ and the IP is inside of $e$. 
Therefore we keep a separate list $J$ of IPs to deal with this case.

@@

  \SetKw{And}{And}
  \DontPrintSemicolon
  \KwIn{$I$ with IPs on $S_3$ boundary, partially filled $F$}
  \KwOut{all IPs in $I$, complete $F$}
